---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

The activity.csv in the current folder is loaded
```{r,echo=TRUE}
activity <- read.csv('activity.csv')
```


## What is mean total number of steps taken per day?

```{r,echo=TRUE}
summary(activity$steps)
hist(activity$steps)
totalSteps <- sum(activity$steps,na.rm=TRUE)
print(totalSteps)
meanSteps <- mean(activity$steps,na.rm=TRUE)
print(meanSteps)
medianSteps <- median(activity$steps,na.rm=TRUE)
print(medianSteps)
```
## What is the average daily activity pattern?
```{r,echo=TRUE,warning=FALSE}
aggregateSteps <- aggregate(activity,list(activity$interval),mean,na.rm=TRUE)
plot(aggregateSteps$interval,aggregateSteps$steps,type="l")
maxSteps <- which.max(aggregateSteps$steps)
aggregateSteps[maxSteps,]["interval"]
```
## Imputing missing values

0 is the most common value so it is assumed for the NA

```{r,echo=TRUE}
colSums(is.na(activity))
numSteps <- subset(activity,!is.na(activity$steps))
naSteps <- subset(activity,is.na(activity$steps))
str(numSteps)
str(naSteps)
for(i in seq(1:dim(naSteps))){
  naSteps[i,"steps"] <- 0
  }
str(naSteps)
stepsImputed <- rbind(numSteps,naSteps)
str(stepsImputed)
byDate <- tapply(stepsImputed$steps,stepsImputed$date,sum)
hist(byDate)
# mean steps by date
tapply(stepsImputed$steps,stepsImputed$date,mean)

# median steps by date
tapply(stepsImputed$steps,stepsImputed$date,median)
```
Looks like doing a simple imputation as above had a major impact on the data. Need a better approach for this. 

## Are there differences in activity patterns between weekdays and weekends?
